Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-11-10 Paper/ms.tex
parameters

The unknown parameters are:
\begin{eqnarray}
\left\{N, \boldsymbol{\alpha}, \{\boldsymbol{\phi}\}_{i=1}^N, y_0, s, \nu\right\}
\end{eqnarray}
where $\boldsymbol{\alpha} = \{\mu_T, \sigma_T, \mu_A\}$ are the
hyperparameters, and $\phi_i = \{\}$ are the properties of planet $i$.

@@

>>>>

@@

To fit a planet model to radial velocity data, we need parameters to describe
the properties of each planet. We also include

The unknown parameters are:
\begin{eqnarray}
\left\{N, \boldsymbol{\alpha}, \{\boldsymbol{\psi}\}_{i=1}^N, y_0, s, \nu\right\}
\end{eqnarray}
where $N$ is the number of planets,
$\boldsymbol{\alpha} = \{\mu_T, \sigma_T, \mu_A\}$ are the
hyperparameters used to define the prior for the properties of the planets,
and $\psi_i = \{T_i, A_i, \phi_i, v_i, \theta_i\}$
are the properties of planet $i$.
The parameter $y_0$ describes a DC offset in the data, and $s$ and $\nu$ are
parameters allowing for a non-gaussian distribution for the noise in the
measurements.
